---
title: "Untitled"
author: "Yulun Chen"
date: "2026-07-015"
output: html_document
---

```{r}

```{r}
trainX <- read.table("./UCI HAR Dataset/train/X_train.txt")
trainY <- read.table("./UCI HAR Dataset/train/y_train.txt")
train_subject <- read.table("./UCI HAR Dataset/train/subject_train.txt")



testX <- read.table("./UCI HAR Dataset/test/X_test.txt")
testY <- read.table("./UCI HAR Dataset/test/y_test.txt")
test_subject <- read.table("./UCI HAR Dataset/test/subject_test.txt")


data_X= rbind(trainX,testX)
data_Y=rbind(trainY,testY)
data_subject=rbind(train_subject,test_subject)



features <- read.table("./UCI HAR Dataset/features.txt")



activity_labels <- read.table("./UCI HAR Dataset/activity_labels.txt")
colnames(activity_labels) <- c("ActivityID", "ActivityType")


colnames(data_X) <- features[, 2]
colnames(data_Y) <- "ActivityID"
colnames(data_subject) <- "SubjectID"


Mean_Std <- grepl("mean\\(\\)|std\\(\\)", colnames(data_X))
Main_data_X=data_X[,Mean_Std]

# Here is the clean data

Clean_data=cbind(data_subject,data_Y,Main_data_X)



Clean_Data=merge(activity_labels,Clean_data, by="ActivityID", all.x=TRUE)



colnames(Clean_Data) <- gsub("Mag", "Magnitude", colnames(Clean_Data))
colnames(Clean_Data) <- gsub("BodyBody", "Body", colnames(Clean_Data))
colnames(Clean_Data) <- gsub("^t", "time", colnames(Clean_Data))
colnames(Clean_Data) <- gsub("^f", "frequency", colnames(Clean_Data))
colnames(Clean_Data) <- gsub("Acc", "Accelerometer", colnames(Clean_Data))
colnames(Clean_Data) <- gsub("Gyro", "Gyroscope", colnames(Clean_Data))

library(dplyr)
Final_Set <- Clean_Data %>%
  group_by(SubjectID, ActivityID, ActivityType) %>%
  summarise_all(mean)

library(tidyverse)
write_tsv(Final_Set, "Final_Set.txt")
```




